\section{Glossary of Terms}
\label{app:glossary}

\begin{description}
\item[Reuleaux triangle]
Intersection of three circles of equal radius $s$ centred at the vertices of an
equilateral triangle. Constant width $s$.

\item[Generating circles]
The three full circles of radius $s$ retained as geometrically real throughout
the construction (not discarded after the boundary arcs are drawn). This is the
foundational assumption of the framework.

\item[Force Angle]
The opening angle formed at a vertex by any two generating circles:
\[
\theta(d)=\frac{2\pi}{3}-2\arcsin\Bigl(\frac{d}{2s}\Bigr),\qquad d\in[0,s\sqrt{3}].
\]
Approaches but never reaches $120^\circ$ for finite $d>0$. Formerly called the
Fork Angle; renamed to emphasise its role as the seat of residual mechanical force.

\item[Angular Shortfall (Energetic loss)]
The permanent angular deficit from perfect three-fold closure:
\[
\Delta\theta(d)=2\arcsin\Bigl(\frac{d}{2s}\Bigr)>0\quad\text{for all }d>0.
\]
Critical value at the tetrahedral edge ($d=s$): $\Delta\theta_c=\pi/3$.
Root cause of residual stress, residual angular momentum, and cyclicity.

\item[Pressure Shell]
The four-sphere shell formed when three circles are lifted to four spheres of
radius $s$ at the vertices of a regular tetrahedron of side $s$. Inner radius
$(1-\sqrt{6}/4)s$, outer radius $(1+\sqrt{6}/4)s$, thickness $(\sqrt{6}/2)s$.
Formerly called the membrane body.

\item[Extended nucleus]
The layered composite object formed by the Pressure Shell:
\begin{itemize}
\item \textbf{Heart} --- maximal 4-of-4 overlap (core, strongest bonding);
\item \textbf{Skin} --- predominantly 3-of-4 overlap (transitional);
\item \textbf{Pressure Shell} --- 1-of-4 or 2-of-4 overlap (imperfect, leaky outer layer).
\end{itemize}
Formerly called the layered particle.

\item[Residual stress]
Mechanical expression of the Angular Shortfall:
\[
\sigma_{\mathrm{res}}=\kappa\cdot\Delta\theta,\qquad\kappa\neq 0.
\]

\item[Residual-stress dipole]
The two opposite signs forced by the shortfall:
$P>0$ (tension / stretch) and $p<0$ (pressure / compression).
Neither sign may vanish while the shortfall exists.

\item[Pressure length $\ell$]
Pure geometric distortion scale (no stress symbol required):
\[
\ell=\frac{s}{\sqrt{10}}\quad\text{(pressure length; pure geometry)}.
\]
Derived from critical strain $\varepsilon_c=1/\sqrt{10}$. Distinct from residual stress $\sigma_{\mathrm{res}}$.

\item[Pressure--length comparison]
Primary axis $\mathrm{P}\ell \leftrightarrow \ell\mathrm{P}$ (pressure greater than length $\leftrightarrow$ length greater than pressure).

\item[Pressure-length regimes]
Combinatorial states of residual pressure relative to $\ell$:
$\mathrm{pp}$ (highest compression), $\mathrm{pl}$ / $\mathrm{P}\ell$ (strong compression),
$\mathrm{pL}$ / $\ell\mathrm{P}$ (length-led), $\mathrm{PL}$ (balanced positive),
$\mathrm{pl}$ (balanced negative), $\mathrm{PP}$ (highest stretch), $\mathrm{Pl}$ (moderate stretch).

\item[Elastic moduli]
Young-type, bulk and shear ratios fixed by tetrahedral geometry:
\[
Y=\sqrt{10}\,|\sigma_{\mathrm{res}}|,\quad
K=\frac{\sqrt{10}}{3}\,|\sigma_{\mathrm{res}}|,\quad
G=\frac{3}{\pi}\,|\sigma_{\mathrm{res}}|.
\]

\item[Inertial mass]
\[
m\sim\frac{\hbar}{c\,s}.
\]
With $s\approx 0.84\,\mathrm{fm}$ this yields hadronic-scale mass.

\item[Residual angular momentum]
\[
\mathbf{L}_{\mathrm{res}}\propto\kappa\cdot\Delta\theta\times\mathbf{r}.
\]
The Angular Shortfall acting at a lever arm produces permanent rotational bias
(honeycombing, vortex action, Pressure Shell spin).

\item[Critical contact number]
\[
N_c^*=3.
\]
Minimum membrane--membrane contacts for aggregation; below this the dissolution
pathway is open.

\item[Aggregation pathway]
$N_c\ge 3$: residual tension couples contacting membranes into larger composite
structure (including Boerdijk--Coxeter helical growth).

\item[Dissolution pathway]
$N_c<3$: ordered layering is lost; capacity returns to the ambient field.

\item[Five optical modes]
Geometric regimes of residual electromagnetic organisation controlled by the
shortfall: Caustic (hyper-concentrated focus), Prismatic (dispersion),
Kinetic (living intermediate residual; seat of $P/p$), Scotopic (dim),
Cryptic (flat diffusion).

\item[Dual dissipation]
Caustic channel $=$ energetic; solvent boundary $=$ sympathetic transfer across
opposing residual domains.

\item[Boerdijk--Coxeter helix]
Face-to-face stacking of tetrahedra:
\[
\theta_{BC}=\arccos(-2/3),\quad H=\frac{s}{\sqrt{10}},\quad R=\frac{3s\sqrt{3}}{10}.
\]

\item[Cyclicity]
Forced by the Angular Shortfall: no configuration reaches perfect static
equilibrium. The system evolves through flattening, saturation, residual release
and renewed propagation.

\item[Strong nuclear field]
Primordial bonding capacity of the universe; taken as primitive. Its geometric
signature is the permanent shortfall in three-fold closure.
\end{description}
